\documentclass[11pt]{article}

\usepackage[letterpaper,margin=0.65in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{ebgaramond}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Header setup
\pagestyle{fancy}

% Clear defaults
\fancyhf{}

% Name + page number on top right
\fancyhead[R]{\small Francy D. Luna Diaz \,|\, \thepage}

% Remove header rule (optional)
\renewcommand{\headrulewidth}{0pt}

% More room for header
\setlength{\headheight}{14pt}


\pagenumbering{arabic}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Zoe-style left section column
\newlength{\leftcol}
\setlength{\leftcol}{1.05in}

\newlength{\rightcol}
\setlength{\rightcol}{\dimexpr\textwidth-\leftcol-0.22in\relax}

\newcommand{\cvsection}[2]{%
\vspace{0.85em}
\noindent
\begin{minipage}[t]{\leftcol}
\raggedright\bfseries #1
\end{minipage}
\hspace{0.35in}
\begin{minipage}[t]{\rightcol}
#2
\end{minipage}
\par
}

\newcommand{\entry}[1]{%
\hangindent=1.25em
\hangafter=1
#1\par\vspace{0.35em}
}

\newcommand{\subhead}[1]{%
\textbf{#1}\par\vspace{0.25em}
}

\newcommand{\schoolentry}[4]{%
\textbf{#1} \hfill #2\par
#3\par
#4\par\vspace{0.45em}
}

\begin{document}
\thispagestyle{empty}


\begin{center}
    {\huge \textbf{Francy D. Luna Diaz}}\par
    505 S State Street, 5755 Haven Hall, Ann Arbor, MI\par
    Email: \href{mailto:LunaDiaz@UMich.edu}{LunaDiaz@UMich.edu}\\
    Website: \url{https://francylunadiaz.com}
\end{center}


\cvsection{EDUCATION}{
\schoolentry{University of Michigan}{Expected May 2027}
{Ph.D., Political Science}
{Dissertation: \textit{Rumors Across Borders: The Influence of Transnational Ties on the Information Environments and Political Attitudes of Latinos.}\\
Committee: Nicholas Valentino (Chair), Ted Brader, Mara Ostfeld, Yanna Krupnikov, Charles Shipan}

\schoolentry{University of Arizona}{May 2019}
{B.A., Political Science, B.A., Law}
{4.00 GPA, \textit{summa cum laude}, Highest Honors}

\schoolentry{Pima Community College}{May 2016}
{A.A., Political Science}
{4.00 GPA, Highest Honors}
}

\vspace{-0.45em}

\cvsection{RESEARCH INTERESTS}{
Latino politics, race and ethnic politics, public opinion, political communication, misinformation, transnationalism, social media, mixed methods
}
\vspace{0.45em}

\cvsection{PUBLICATIONS}{
\subhead{Peer-Reviewed Articles}

\entry{``Women `doing' the judiciary: Rethinking the justice argument for descriptive representation.'' (With Suzzane Dovi), 2020. \textit{Politics, Groups, and Identities}, 8(4), 790--802. Dialogues Paper, Routledge. \url{https://doi.org/10.1080/21565503.2020.1789882}}

\subhead{Public Scholarship}

\entry{``Some Findings about the Nature and Distribution of American Stereotypes About Americans: Evidence from a 2024 US Survey.'' (with Mark Tessler and Amnon Cavari), 2025. \textit{Center for Political Studies Blog}. Research Brief. Ann Arbor: University of Michigan Center for Political Studies, Institute for Social Research. \url{https://cpsblog.isr.umich.edu/wp-content/uploads/2025/10/American-Stereotypes-1025-Remediated.pdf}}

\entry{``Latinos for Trump in 2020.'' (with Tevah Platt), 2022. \textit{Center for Political Studies Blog}. Blog. Ann Arbor: University of Michigan Center for Political Studies, Institute for Social Research. \url{https://cpsblog.isr.umich.edu/?p=3106}}
}

\cvsection{MANUSCRIPTS}{

\subhead{Dissertation}
\entry{\textit{Book-Style Dissertation}: ``Rumors Across Borders: The Influence of Transnational Ties on Latinos’ Information and Misinformation Environment.''}

\subhead{Under Review}
\entry{``Rumors Across Borders: How Transnational Ties and Social Media Shape Latino Belief in Misinformation and Support for Trump.''} 

\entry{``Mobilizing Anger in Local School Board Politics'' (with Hilary Izatt and Zoe C. Walker).}

\subhead{Working Papers}
\entry{``What Changed? Predictors of the Latino Vote Shift During the Trump Era'' (with Mario Villegas, Franshelly Martinez-Ortiz, and Nicholas Valentino).}}
\cvsection{\textcolor{white}{Manuscripts}}{
\entry{``Lost in Translation: Language and Perception of Misinformation for Latinos in the U.S.'' (with Franshelly Martinez-Ortiz).}

\subhead{Works in progress}
\entry{``Threats Against Democracy, Anger, and Mobilization for the 2024 Presidential Election'' (with Nicholas Valentino and Hilary Izatt).}

\entry{``Effect of Racial Labels on Survey Responses'' (with Sunshine Hillygus and Nicholas Valentino)}

\entry{``The rACE Coding Scheme: Measuring Racial Attribution, Color-Blindness, and Explicitness in Open-Ended Survey Responses''}

\entry{``Conspiratorial Thinking and Anti-Semitism, Islamophobia, and Anti-Black Sentiment in the U.S.'' (with Mark Tessler and Amnon Cavari).}

}

\vspace{0.45em}

\cvsection{CONFERENCE PRESENTATIONS}{
\entry{``Mobilizing Anger in Local School Board Politics.'' 2026. Invited to present at Midwest Political Science Association.}

\entry{``Rumors Across Borders: The Impact of Transnational Ties on Latino Information Environments and Political Attitudes.'' 2024. Presented at PRIEC UT Austin, PRIEC MSU, Western Political Science Association Latina/o/x Politics Workshop, Midwest Political Science Association, International Society of Political Psychology, and American Political Science Association Annual Meeting.}

\entry{``Lost in Translation: Language and Perception of Misinformation for Latinos in the U.S.'' 2024. Presented at the International Society of Political Psychology and American Political Science Association Annual Meeting.}

\entry{``Latinos for Trump in 2020: A Story of Heterogeneous Information Environments and Social Media.'' 2023. Presented at Western Political Science Association Latina/o/x Politics Workshop, Midwest Political Science Association, and International Society of Political Psychology.}

\entry{``In Their Own Words: Latino Vote and Preference for the 2016 and 2020 Presidential Elections.'' 2022. Presented at International Society of Political Psychology Annual Meeting and American Political Science Association Annual Meeting.}
}
\vspace{0.45em}

\cvsection{TEACHING}{
\entry{Congress and the Presidency, Graduate Student Instructor (Fall 2025, Spring 2026) \\
Instructor: Lynn Rivers.}

\entry{Congress and the Presidency, Grader (Spring 2023 to Spring 2025) \\ Instructor: Lynn Rivers.}

\entry{The Legislative Process, Graduate Student Instructor (Spring 2021)\\ Instructor: Christian Fong.}

\entry{Introduction to American Politics, Graduate Student Instructor (Fall 2020)\\ Instructor: Charles Shipan.}
}
\vspace{0.45em}

\cvsection{INVITED TALKS AND LECTURES}{
\entry{Stonehill College, Intro to American Politics, Professor Guillermo Caballero (October 2024)}

\entry{Binghamton University (SUNY), Research Laboratory, Professor Hilary Izatt (September 2024)}

\entry{University of Massachusetts Amherst, Survey Methods Graduate Seminar, Professor Alexander Theodoridis (April 2023)}
}
\vspace{0.45em}

\cvsection{GRANTS}{

\subhead{Individual}
\entry{CEW+ Center for the Education of Women, \textit{Career Development Grant}, \$2,000 (2026)}
\entry{NSF APSA DDRIG \textit{Doctoral Dissertation Research Improvement Grant}, \$15,000 (2025)} 
\entry{American Political Science Association, \textit{Fund for Latino Scholarship Grant}, \$1,500 (2024)}
\entry{University of Michigan, \textit{Rackham Graduate Research Grant} (2024)}
\entry{American Political Science Association, \textit{First Generation Scholar Grant} (2022)}

\subhead{Co-Authored}
\entry{American Political Science Association, \textit{Spring Centennial Grant}, \$2,500 (2024)}
\entry{National Center for Institutional Diversity, Rackham Graduate School, and the Center for Racial Justice at the Gerald R. Ford School of Public Policy, \textit{Anti-Racism Graduate Research Grant}, \$15,000 (2023)}

\entry{American Political Science Association, \textit{Spring Centennial Grant}, \$2,500 (2023)}
}
\vspace{0.45em}

\cvsection{FELLOWSHIPS \& AWARDS}{
\subhead{NSF}
\entry{NSF GRFP National Science Foundation Graduate Research Fellowship (2021-2026)}
\vspace{0.35em}

\subhead{University of Michigan}
\entry{Rackham Merit Fellowship (2019-2026)}
\entry{CEW+ Center for the Education of Women+, Gutsy Broad Fund Fellowship (2025)}
\entry{Garth Taylor Fellowship in Public Opinion (2025)}
\entry{Hanes Walton Jr. Fellowship for Graduate Study in Racial and Ethnic Politics (2024)}
\entry{Philip Converse and Warren Miller Fellowship in American Political Behavior (2023)}
\vspace{0.35em}

\subhead{American Political Science Association}
\entry{APSA Diversity Fellowship (2020)}

\subhead{Other}
\entry{AAPOR American Association for Public Opinion Research, \textit{Student-Faculty Diversity Pipeline Award} (2024)}

\entry{University of Arizona \textit{Robie Gold Medal Award} (2019)}

\entry{University of Arizona \textit{Honors College Outstanding Senior} (2019)}

\entry{University of Arizona UROP Undergraduate Research Opportunity Program Scholar (2018)}

\entry{Pima Community College Commencement Speaker (2016)}
}
\vspace{0.45em}

\cvsection{SERVICE}{
\entry{Article Reviewer, American Journal of Political Science (2026)}

\entry{Dissertation Writing Workshop Leader (2026)}

\entry{Undergraduate Honors Thesis Committee Member, Political Science Department (2021, 2024, 2026)}

\entry{Research Workshop Coordinator, Interdisciplinary Race and Ethnic Politics Workshop (2022 to 2024)}

\entry{Graduate Student Member of the Hiring Committee, Faculty Search for the Political Science Methodology Subfield, University of Michigan (2023)}

\entry{Application Reviewer, Master of Data Science Program, University of Michigan (2023, 2024)}

\entry{Admissions Assistant, Emerging Scholars Conference (October 2022 and October 2024)}

\entry{Research Workshop Coordinator, Interdisciplinary Workshop in American Politics (2021, 2022)}
}
\vspace{0.45em}

\cvsection{RESEARCH EXPERIENCE}{
\entry{Graduate Research Assistant, ANES American National Election Studies. Current.}

\entry{Graduate Research Assistant, Professors Mark Tessler and Amnon Cavari (2024)}

\entry{Graduate Research Assistant, Professor Ted Brader (2020)}

\entry{Graduate Research Assistant, Professor Charles Shipan (2020)}

\entry{Undergraduate Research Assistant, Professors Javier Osorio and Susan Brewer-Osorio (2018 to 2019)}

\entry{Undergraduate Research Assistant, Professor Suzanne Dovi (2017)}

\entry{Research Fellow, Undergraduate Research Opportunity Consortium, Professor Samara Klar (2017)}
}
\vspace{0.45em}

\cvsection{MENTORSHIP \& RESEARCH SUPERVISION}{
\entry{Undergraduate Research Supervisor (2023-2026)}
\entry{Graduate Student Mentor (2020-2023)}
\entry{Fellowship Application Mentor (2021, 2022, 2026)}
}
\vspace{0.45em}

\cvsection{METHODS TRAINING}{

\entry{Advanced Quantitative Methods. Instructor: Walter Mebane (Fall 2021)}

\entry{Behavioral Research Methods. Instructor: Nicholas Valentino (Fall 2021)}

\entry{Statistics Methods Research II. Instructor: Kevin Quinn (Winter 2020)}

\entry{Statistics Methods Research I. Instructor: Yuki Shiraito (Fall 2020).}
}
\vspace{0.45em}

\cvsection{PROFESSIONAL AFFILIATIONS}{
American Political Science Association\par
Midwest Political Science Association\par
International Society of Political Psychology\par 
International Political Science Association\par
American Association for Public Opinion Research
}
\vspace{0.45em}

\cvsection{SKILLS}{
\entry{\textbf{Methodological Expertise:} Survey design and implementation, survey experiment design and pre-registration, quantitative and qualitative data analysis, mixed-methods research, computational text analysis, LLM-assisted text classification, and interviews.}

\entry{\textbf{Software:} R, Stata, Qualtrics, \LaTeX, Dedoose.}

\entry{\textbf{Languages:} English (Native), Spanish (Native).}
}

\end{document}